---
title: "Indian Treaties Workspace"
output: html_notebook
---
#Text Reuse, Clustering

This notebook will explore text reuse in Indain treaties at the paragraph level and clustering at the paragraph and document level.First, some general information regarding Indian treaties is explored. 
```{r}
library(rvest)
library(magrittr)
library(tidyverse)
library(stringr)
library(pbapply)
library(parallel)
library(textreuse)
library(dplyr)
library(igraph)
library(ggplot2)
library(stringr)
library(data.table)
library(Matrix)
library(tokenizers)
library(text2vec)
library(broom)
library(apcluster)
library(readr)
library(GGally)
library(intergraph)
library(ggraph)
```
###General Analysis


```{r}
#dtm2 is generated below.

parsed_treaties <- readRDS("parsed_treaties.rds")
addyear <- basename(parsed_treaties$file) %>% str_replace("\\.htm", ".txt")


parsed_treaties <- parsed_treaties %>% 
  mutate(document_id = basename(parsed_treaties$file) %>% str_replace("\\.htm", ".txt"))

#dtm2 <- dtm2 %>%
#  mutate(document_id = rownames(dtm2))
         
  
dtm_to_df <- function(x, words) {
  stopifnot(is.character(words))
  out <- as_tibble(as.data.frame(as.matrix(x[, words])))
  colnames(out) <- words
  ids <- str_replace_all(rownames(x), "\\.txt", "")
  ids <- str_split_fixed(ids, "-", n = 2)
  out %>% 
    mutate(document_id = ids[ , 1, drop = TRUE])
          }
  
words_of_interest <- c("horse", "indian", "death", "buffalo")

counts <- dtm_to_df(dtm2, words_of_interest) %>% 
  gather(word, count, -document_id) %>% 
  filter(count > 0)

item_years <- parsed_treaties %>% 
  select(document_id, year)

counts %>% 
  group_by(document_id, word) %>% 
  summarize(count = sum(count)) %>% 
  left_join(parsed_treaties, by = "document_id") %>% 
  group_by(year, word) %>% 
  summarize(count = sum(count)) %>% 
  ggplot(aes(x = year, y = count, color = word)) +
  geom_point() +
  geom_smooth(span = 0.1, se = FALSE) +
  labs(title = "A Title") + 
  xlim(1760,1890)
```


###Creating the Corpus without Minhashes
```{r createcorpus, cache=TRUE}
corpus <- TextReuseCorpus(list.files("C:/Users/Joshua/Documents/rdata/indian_treaties/treaty-paragraphs", 
                   pattern = "*.txt",
                   full.names = TRUE), tokenizer = tokenize_ngrams, n = 5,
                          progress = FALSE)
#saveRDS()
```

###Creating the Corpus with Minhashes

```{r createcorpus2, cache=TRUE}
minhash <- minhash_generator(n = 40, seed = 3552)

corpus2 <- TextReuseCorpus(list.files("C:/Users/Joshua/Documents/rdata/indian_treaties/treaty-paragraphs", 
                   pattern = "*.txt",
                   full.names = TRUE), tokenizer = tokenize_ngrams, n = 5,
                          minhash_func = minhash, keep_tokens = TRUE,
                          progress = FALSE)

wc <- wordcount(corpus2)

corpus2 <- corpus2[wc >= 40]

#saveRDS(corpus2, "minhashed_corpus_par_level.rds")
#corpus2 <- readRDS("minhashed_corpus_par_level.rds")
```



```{r}
lsh_threshold(h = 40, b = 20)

buckets <- lsh(corpus2, bands = 20, progress = FALSE)
buckets
```

###Finding Candidates
```{r}
#matches <- lsh_query(buckets, "19000630400")
#matches

candidates <- lsh_candidates(buckets)

#saveRDS(candidates,"candidates_par_level.rds")
#candidates <- readRDS("candidates_par_level.rds")
 
```

### Comparing Candidates

Filtering out the candidates that turned out not to be matches. 
```{r}

similarities <-lsh_compare(candidates, corpus2, jaccard_similarity)

similarities <- filter(similarities, score> .2)

get_treaty <- function(x) {
  str_sub(x, 1, 7)
}

similarities2 <- similarities %>% 
        mutate(treaty_a = get_treaty(a),
        treaty_b = get_treaty(b)) %>% 
        count(treaty_a, treaty_b) %>% 
        arrange(desc(n)) %>% 
        filter(treaty_a != treaty_b) 
        

#Add years to similarities
parsed_treaties <- readRDS("parsed_treaties.rds")

parsed_treaties <- parsed_treaties %>% 
  mutate(document_id = basename(parsed_treaties$file) %>% str_replace("\\.htm", "")) %>%
  mutate(document_id_a = basename(parsed_treaties$file) %>% str_replace("\\.htm", "")) %>%
  mutate(document_id_b = basename(parsed_treaties$file) %>% str_replace("\\.htm", ""))

similarities2 <- similarities2 %>%
              mutate(document_id_a = treaty_a) %>%
              mutate(document_id_b = treaty_b) 
              
similarities2 <- left_join(parsed_treaties, similarities2, by = "document_id_a")

similarities2 <- subset(similarities2, select = -c(1, 2, 3, 4))

similarities2 <- similarities2 %>% 
                mutate(treaty_a_year = year)


similarities2 <- subset(similarities2, select = -c(1, 2, 3, 4))

similarities2 <- similarities2 %>%
                mutate(document_id_b = document_id_b.y)

similarities2 <- subset(similarities2, select = -c(4))

similarities2 <- left_join(parsed_treaties, similarities2, by = "document_id_b")

similarities2 <- similarities2 %>% 
                mutate(treaty_b_year = year)

similarities2 <- subset(similarities2, select = -c(1, 2, 3, 4, 5, 6, 7, 8))

similarities2 <- na.omit(similarities2)

similarities2 <- similarities2 %>%
                    mutate(borrow_span = (treaty_a_year - treaty_b_year))

#saveRDS(similarities, "similarities.rds")
#saveRDS(similarities2, "similarities2.rds")

#similarities <- readRDS("similarities.rds")
#similarities2 <- readRDS("similarities2.rds")

fd_matches <- similarities2

#saveRDS(fd_matches, "fd_matches.rds")
#fd_matches <- readRDS("fd_matches.rds")

```

Histogram of similarities
```{r} 
hist(similarities$score, breaks = 100) 
```

```{r}
paragraph_network <- similarities %>% 
  mutate(treaty_a = get_treaty(a),
         treaty_b = get_treaty(b)) %>% 
      filter(treaty_a != treaty_b)
```


```{#r}
#Old Code

matches %>% 
  mutate(treaty_a = get_treaty(a),
         treaty_b = get_treaty(b)) %>% 
  count(treaty_a, treaty_b) %>% 
  arrange(desc(n)) %>% 
  filter(treaty_a != treaty_b) %>%
   View


fd_matches =  (matches %>% mutate(treaty_a = get_treaty(a),
         treaty_b = get_treaty(b)) %>% 
  count(treaty_a, treaty_b) %>% 
  arrange(desc(n)) %>% 
  filter(treaty_a != treaty_b)) 
```

##Networks

###Paragraph Level Borrowing
The following graph displays treaty borrowing at the paragraph level.
```{r}

similarities_par <- similarities %>%
              mutate(document_id_a = a) %>%
              mutate(document_id_b = b) 
              
parsed_treaties <- readRDS("parsed_treaties.rds")

parsed_treaties <- parsed_treaties %>% 
  mutate(document_id = basename(parsed_treaties$file) %>% str_replace("\\.htm", "")) %>%
  mutate(document_id_a = basename(parsed_treaties$file) %>% str_replace("\\.htm", "")) %>%
  mutate(document_id_b = basename(parsed_treaties$file) %>% str_replace("\\.htm", ""))

similarities_par <- left_join(parsed_treaties, similarities_par, by = "document_id_a")

similarities_par <- subset(similarities_par, select = -c(1, 2, 3, 4))

similarities_par <- similarities_par %>% 
                mutate(treaty_a_year = year)


similarities_par <- subset(similarities_par, select = -c(1, 2, 3, 4))

similarities_par <- similarities_par %>%
                mutate(document_id_b = document_id_b.y)

similarities_par <- subset(similarities_par, select = -c(4))

similarities_par<- left_join(parsed_treaties, similarities_par, by = "document_id_b")

similarities_par <- similarities_par %>% 
                mutate(treaty_b_year = year)

similarities_par <- subset(similarities_par, select = -c(1, 2, 3, 4, 5, 6, 7, 8))

ssimilarities_par <- na.omit(similarities_par)

similarities_par <- similarities_par%>%
                    mutate(borrow_span = (treaty_a_year - treaty_b_year))








sample_graph2 <- graph.data.frame(paragraph_network,directed = FALSE)

plot(sample_graph2, 
     layout = layout.auto,
    #vertex.label.cex = 0.7,
    vertex.label = NA,
    margin = 0,
    vertex.size = 1,
      main = "Network Graph of Paragraph Borrowing",
    edge.width = similarities$score)

```
###Decomposing the Paragraph Network

The following graph represents the largest cluster from above.
```{r}
components <-decompose(sample_graph2, mode = c("weak", "strong"), max.comps = NA,
  min.vertices = 5)

components_1_graph <- (components[[1]])

plot(components[[1]],
     layout = layout.auto,
    vertex.label.cex = 0.7,
    #vertex.label = NA,
    margin = -0,
    vertex.size = 1,
    main = "Network Graph of Largest Paragraph Cluster",
    edge.width = similarities$score)
```

###Treaty Borrowing at the Document Level

The following are network graphs of the treaties with the edges representing the number of shared paragraphs. 
```{r}
parsed_treaties2 <- readRDS("parsed_treaties.rds")

parsed_treaties2 <- parsed_treaties2 %>%
      mutate(document_id = basename(parsed_treaties2$file) %>% str_replace("\\.htm", ""))

node_df <- subset(parsed_treaties2, select = -c(1, 2, 3, 4))
          
node_df <- node_df[, c(2,1)]

node_df <- node_df %>%
          mutate(treaty_lookup = document_id )

node_df <- node_df %>%
          mutate(decade = year %>% str_extract("\\d{3}"))

node_att_graph <- graph_from_data_frame(d = fd_matches, vertices = node_df, directed = FALSE)

#saveRDS(node_att_graph, "node_att_graph.rds")
#node_att_graph <- readRDS("node_att_graph.rds")

sample_graph <- node_att_graph

#saveRDS(sample_graph, "sample_graph.rds")
#sample_graph <- readRDS("sample_graph.rds")  

#Old way to create igraph = graph.data.frame(fd_matches,directed = FALSE)

plot(sample_graph, 
     layout = layout.auto,
    #vertex.label.cex = 0.7,
    vertex.label = NA,
    margin = -0,
     vertex.size = 3,
    main = "Network Graph of Treaty Borrowing",
    edge.width = fd_matches$n >2)
    
```


```{#r}

#Trial to recreate igraph with node attributes

parsed_treaties2 <- readRDS("parsed_treaties.rds")

parsed_treaties2 <- parsed_treaties2 %>%
      mutate(document_id = basename(parsed_treaties2$file) %>% str_replace("\\.htm", ""))

node_df <- subset(parsed_treaties2, select = -c(1, 2, 3, 4))
          
node_df <- node_df[, c(2,1)]


node_att_graph <- graph_from_data_frame(d = fd_matches, vertices = node_df, directed = FALSE)


plot(node_att_graph)

G <- node_att_graph

V(G)$color <- ifelse(V(G)$year =="1865", "lightblue", "orange")

plot(G, 
     layout = layout.auto, 
     vertex.size = 4, 
     vertex.label = NA, 
     edge.width = fd_matches$n >2)    

colrs <- c("red", "orange")
V(G)$color <- colrs[V(G)$treaty_a_year == "1865"]

#Attempt to seperate by decade
#seventeen_eighties <- filter(fd_matches, treaty_a_year == c(1780:1789))
                       
                       #| treaty_b_year == c(1780:1789))


```

 
```{r}
G <- node_att_graph

#V(G)$color <- ifelse(V(G)$year > 1820 & V(G)$year< 1829, "lightblue", "orange") 

V(G)$color <- ifelse(V(G)$decade == "177", "blue", ifelse(V(G)$decade == "178","cyan", ifelse(V(G)$decade == "179","darkmagenta", ifelse(V(G)$decade == "180","darkgreen", ifelse(V(G)$decade == "181","green", ifelse(V(G)$decade == "182","orange", ifelse(V(G)$decade == "183","springgreen2", ifelse(V(G)$decade == "184","red", ifelse(V(G)$decade == "185","hotpink", ifelse(V(G)$decade == "186","yellow", ifelse(V(G)$decade == "187","black", ifelse(V(G)$decade == "188","tan", "white" ))))))))))))
plot(G, 
     layout = layout.auto,
     vertex.label.cex = 0.6,
     vertex.label.dist =0,
     vertex.label.degree = pi,
     vertex.size = 4, 
     margin = 0,
     #vertex.label = NA, 
     main = "Network Graph of Treaty Borrowing",
     edge.width = fd_matches$n)
legend(x=-2, y=1., c("1770s","1780s", "1790s","1800s", "1810s", "1820s", "1830s", "1840s", "1850s", "1860s", "1870s", "1880s"),  pch=21, pt.cex=2, cex=.8, title="Decades",
       pt.bg=c("blue", "cyan", "darkmagenta", "darkgreen", "green", "orange", "springgreen2", "red", "hotpink","yellow", "black", "tan"))
```
Showing the 1854 and 1855 Chippewa Treaties
```{r}
chi_1854 <- sample_graph

#saveRDS(chi_1854, "chi_1854.rds")
#chi_1854 <- readRDS("chi_1854.rds")

V(chi_1854)$color <- ifelse(V(chi_1854)$name == "chi0648", "red", ifelse(V(chi_1854)$name == "chi0685","blue", ifelse(V(chi_1854)$name == "ott0725","green", "white")))

plot(chi_1854, 
     layout = layout.auto,
    vertex.label.cex = 0.7,
    #vertex.label.color =  ifelse(V(sample_graph)$name == "chi0648", "blue", "black"),
    vertex.label = NA,
    margin = -0,
    vertex.size = 4,
    main = "Selected Chippewa Treaties",
    edge.width = fd_matches$n >5)
legend("left", c("1854 Wisconsin \n (with fishing rights)","1855 Washington \n (w/o fishing rights)", "1855 Detroit \n (with fishing rights)"),  pch=21, pt.cex=2, cex=.8, title="Chippewa Treaties",
       pt.bg=c("red", "blue", "green"))
```
###Decomposing the Document Network
```{r}
components_whole <-decompose(sample_graph, mode = c("weak", "strong"), max.comps = NA,
  min.vertices = 5)

plot(components_whole[[1]],
     layout = layout.auto,
    #vertex.label.cex = 0.6,
    vertex.label = NA,
    margin = -0,
     vertex.size = 1,
    main = "Title",
    edge.width = fd_matches$n >3)

```
The largest cluster:
```{r}
components_whole_1 <- (components_whole[[1]])

plot(components_whole_1, 
     layout = layout.auto,
    #vertex.label.cex = 0.6,
    vertex.label = NA,
    margin = -0.2,
     vertex.size = 1,
    main = "Network Graph of Largest Treaty Cluster",
    edge.width = fd_matches$n)



```
Attempt to split the graph apart futher by removing vertices and the decomposing.

```{r}
broken_graph <- sample_graph

removed_vertices <- c("cre0155", "com0600", "cre0214", "wya0145", "iow0208", "pot0168", "mia0531", "sau0207",  "qua0160")
#removed_edges <- c("osa0095|osa0167")

broken_graph <- delete_vertices(broken_graph, removed_vertices)                 #

#delete_edges(broken_graph, removed_edges) 
 
plot(broken_graph,
     layout = layout.auto,
    vertex.label.cex = 0.6,
    #vertex.label = NA,
    margin = -0.1,
    vertex.size = 1,
    main = "Network Graph of Largest Treaty Cluster",
    edge.width = fd_matches$n >3)

decomposed_broken_graph <-decompose(broken_graph, mode = c("weak", "strong"), max.comps = NA,
  min.vertices = 4)

#saveRDS(decomposed_broken_graph, "decomposed_broken_graph.rds")
#decomposed_broken_graph <- readRDS("decomposed_broken_graph.rds")

plot(decomposed_broken_graph[[2]],
     layout = layout.auto,
    vertex.label.cex = 0.6,
    #vertex.label = NA,
    margin = -0,
     vertex.size = 1,
    main = "Title",
    edge.width = fd_matches$n >2)
```
```{r}

sioux_1865 <- decomposed_broken_graph[[4]]

plot(sioux_1865,
     layout = layout.auto,
    vertex.label.cex = .9,
    vertex.label.dist = 0.9,
    vertex.label.degree = -pi/2,
    #vertex.label = NA,
    margin = .1,
     vertex.size = 20,
    main = "Treaties with Sioux Bands, 1865",
    edge.width = fd_matches$n >2)
#need legend
```
### Network Graphs of Particular Nations
```{r}
similarities3 <- similarities2

get_treaty2 <- function(x) {
  str_sub(x, 1, 3)
}

#similarities3 <- similarities3 %>% 
#        mutate(treaty_a = get_treaty(a),
#        treaty_b = get_treaty(b)) %>% 
#        count(treaty_a, treaty_b) %>% 
#        arrange(desc(n)) %>% 
#        filter(treaty_a != treaty_b) 

similarities3 <- similarities3 %>%
                mutate(nation_a = get_treaty2(treaty_a),
                nation_b =get_treaty2(treaty_b))

#saveRDS(similarities3, "similarities3")
# similarities3 <- readRDS("similarities3")

parsed_treaties2 <- readRDS("parsed_treaties.rds")

parsed_treaties2 <- parsed_treaties2 %>%
      mutate(document_id = basename(parsed_treaties2$file) %>% str_replace("\\.htm", ""))

node_df <- subset(parsed_treaties2, select = -c(1, 2, 3, 4))
          
node_df <- node_df[, c(2,1)]

node_df <- node_df %>%
          mutate(treaty_lookup = document_id)
                 

node_df <- node_df %>%
          mutate(decade = year %>% str_extract("\\d{3}"))

node_df <- node_df %>% 
  mutate(nation = document_id %>% str_sub(1, 3))

#saveRDS(node_df, "node_df")
#node_df <- readRDS("node_df")

```
##Delaware Nation
```{r}

get_nation_del <- filter(similarities3, nation_a %in% "del",
              nation_b %in% "del")

nation_node_del <- filter(node_df, nation %in% "del")

nation_graph_del<- graph_from_data_frame(d = get_nation_del, vertices = nation_node_del, directed = FALSE)

#saveRDS(nation_graph_del, "nation_graph_del.rds")
#readRDS("nation_graph_del.rds")

#nation_graph = graph.data.frame(get_nation, directed = FALSE)

V(nation_graph_del)$color <- ifelse(V(nation_graph_del)$decade == "177", "blue", ifelse(V(nation_graph_del)$decade == "178","cyan", ifelse(V(nation_graph_del)$decade == "179","darkmagenta", ifelse(V(nation_graph_del)$decade == "180","darkgreen", ifelse(V(nation_graph_del)$decade == "181","green", ifelse(V(nation_graph_del)$decade == "182","orange", ifelse(V(nation_graph_del)$decade == "183","springgreen2", ifelse(V(nation_graph_del)$decade == "184","red", ifelse(V(nation_graph_del)$decade == "185","hotpink", ifelse(V(nation_graph_del)$decade == "186","yellow", ifelse(V(nation_graph_del)$decade == "187","black", ifelse(V(nation_graph_del)$decade == "188","tan", "white" ))))))))))))

plot(nation_graph_del, 
     layout = layout.auto,
     vertex.label.cex = 1,
     vertex.label.dist =.9,
     vertex.label.degree = -pi/2,
     vertex.size = 17, 
     margin = 0.3,
     #vertex.label = NA, 
     main = "Network Graph of Delaware Treaty Borrowing",
     edge.width = fd_matches$n)
legend("left", c("1770s","1780s", "1790s","1800s", "1810s", "1820s", "1830s", "1840s", "1850s", "1860s", "1870s", "1880s"),  pch=21, pt.cex=2, cex=.8, title="Decades",
       pt.bg=c("blue", "cyan", "darkmagenta", "darkgreen", "green", "orange", "springgreen2", "red", "hotpink","yellow", "black", "tan"))
```

##Ojibwe

```{r}
get_nation_chi <- filter(similarities3, nation_a %in% "chi",
              nation_b %in% "chi")


nation_node_chi <- filter(node_df, nation %in% "chi")

nation_graph_chi<- graph_from_data_frame(d = get_nation_chi, vertices = nation_node_chi, directed = FALSE)

#saveRDS(nation_graph_chi, "nation_graph_chi.rds")
#readRDS("nation_graph_chi.rds")


E(nation_graph_chi)$color <- "black"

V(nation_graph_chi)$color <- ifelse(V(nation_graph_chi)$decade == "177", "blue", ifelse(V(nation_graph_chi)$decade == "178","cyan", ifelse(V(nation_graph_chi)$decade == "179","darkmagenta", ifelse(V(nation_graph_chi)$decade == "180","darkgreen", ifelse(V(nation_graph_chi)$decade == "181","green", ifelse(V(nation_graph_chi)$decade == "182","orange", ifelse(V(nation_graph_chi)$decade == "183","springgreen2", ifelse(V(nation_graph_chi)$decade == "184","red", ifelse(V(nation_graph_chi)$decade == "185","hotpink", ifelse(V(nation_graph_chi)$decade == "186","yellow", ifelse(V(nation_graph_chi)$decade == "187","black", ifelse(V(nation_graph_chi)$decade == "188","tan", "white" ))))))))))))

plot(nation_graph_chi, 
     layout = layout.auto,
     vertex.label.cex = 1,
     #vertex.label.dist =.9,
    # vertex.label.degree = -pi/2,
     vertex.size = 13, 
     margin = 0.3,
     #vertex.label = NA, 
     main = "Network Graph of Ojibwe Treaty Borrowing",
     edge.width = fd_matches$n >0)
legend("left", c("1770s","1780s", "1790s","1800s", "1810s", "1820s", "1830s", "1840s", "1850s", "1860s", "1870s", "1880s"),  pch=21, pt.cex=2, cex=.8, title="Decades",
       pt.bg=c("blue", "cyan", "darkmagenta", "darkgreen", "green", "orange", "springgreen2", "red", "hotpink","yellow", "black", "tan"))

```

## Cluster Including the 1846 Comanche Treaty

```{r}
decomposed_broken_graph <- readRDS("decomposed_broken_graph.rds")

com_0554_graph <- decomposed_broken_graph[[3]]


V(com_0554_graph)$color <- ifelse(V(com_0554_graph)$decade == "177", "blue", ifelse(V(com_0554_graph)$decade == "178","cyan", ifelse(V(com_0554_graph)$decade == "179","darkmagenta", ifelse(V(com_0554_graph)$decade == "180","darkgreen", ifelse(V(com_0554_graph)$decade == "181","green", ifelse(V(com_0554_graph)$decade == "182","orange", ifelse(V(com_0554_graph)$decade == "183","springgreen2", ifelse(V(com_0554_graph)$decade == "184","red", ifelse(V(com_0554_graph)$decade == "185","hotpink", ifelse(V(com_0554_graph)$decade == "186","yellow", ifelse(V(com_0554_graph)$decade == "187","black", ifelse(V(com_0554_graph)$decade == "188","tan", "white" ))))))))))))

plot(com_0554_graph, 
     layout = layout.auto,
     vertex.label.cex = 0.6,
     vertex.label.dist =0,
     vertex.label.degree = pi,
     vertex.size = 7, 
     margin = -0,
     vertex.label = NA, 
     main = "Treaty Borrowing Cluster including the 1846 Comanche Treaty",
     edge.width = fd_matches$n >2)
legend("left", c("1770s","1780s", "1790s","1800s", "1810s", "1820s", "1830s", "1840s", "1850s", "1860s", "1870s", "1880s"),  pch=21, pt.cex=2, cex=.8, title="Decades",
       pt.bg=c("blue", "cyan", "darkmagenta", "darkgreen", "green", "orange", "springgreen2", "red", "hotpink","yellow", "black", "tan"))
```

```{r}
G2 <- decomposed_broken_graph[[2]]


V(G2)$color <- ifelse(V(G2)$decade == "177", "blue", ifelse(V(G2)$decade == "178","cyan", ifelse(V(G2)$decade == "179","darkmagenta", ifelse(V(G2)$decade == "180","darkgreen", ifelse(V(G2)$decade == "181","green", ifelse(V(G2)$decade == "182","orange", ifelse(V(G2)$decade == "183","springgreen2", ifelse(V(G2)$decade == "184","red", ifelse(V(G2)$decade == "185","hotpink", ifelse(V(G2)$decade == "186","yellow", ifelse(V(G2)$decade == "187","black", ifelse(V(G2)$decade == "188","tan", "white" ))))))))))))

plot(G2, 
     layout = layout.auto,
     vertex.label.cex = 0.6,
     vertex.label.dist =0,
     vertex.label.degree = pi,
     vertex.size = 9, 
     margin = -0,
     #vertex.label = NA, 
     main = "The Manypenny Cluster",
     edge.width = fd_matches$n >2)
legend("left", c("1770s","1780s", "1790s","1800s", "1810s", "1820s", "1830s", "1840s", "1850s", "1860s", "1870s", "1880s"),  pch=21, pt.cex=2, cex=.8, title="Decades",
       pt.bg=c("blue", "cyan", "darkmagenta", "darkgreen", "green", "orange", "springgreen2", "red", "hotpink","yellow", "black", "tan"))
```


Another decomposition with a higher number of minimum vertices.
```{r}
components_whole2 <-decompose(sample_graph, mode = c("weak", "strong"), max.comps = NA,
  min.vertices = 4)

plot(components_whole2[[8]],
     layout = layout.auto,
    vertex.label.cex = 0.6,
    #vertex.label = NA,
    margin = -0,
     vertex.size = 1,
    main = "Network Graph of Largest Treaty Cluster",
    edge.width = fd_matches$n >2)
```
The Sioux Cluster
```{r}
plot(components_whole2[[2]],
     layout = layout.auto,
    vertex.label.cex = 0.6,
    #vertex.label = NA,
    margin = -0,
     vertex.size = 1,
    main = "Sioux Bands Cluster, 1865",
    edge.width = fd_matches$n >3)
```


##PCA at the paragraph level. 
```{r}
#for paragraph level 
files <- list.files("C:/Users/Joshua/Documents/rdata/indian_treaties/treaty-paragraphs",                    pattern = "*.txt",
                  full.names = TRUE)


reader <- function(f) {
  require(stringr)
  n <- parsed_treaties$file %>% str_replace("\\.txt", "")
  doc <- readr::read_file(f)
  names(doc) <- n
  doc
}

it_files <- ifiles(files, reader = reader)
it_tokens <- itoken(it_files,
                   tokenizer = tokenizers::tokenize_words)

vocab <- create_vocabulary(it_tokens)

pruned_vocab <- prune_vocabulary(vocab, term_count_min = 10,
term_count_max = 50000)
vectorizer <- vocab_vectorizer(pruned_vocab)

dtm <- create_dtm(it_tokens, vectorizer)
rownames(dtm) <- basename(files) 

dtmsimilarities <- wordVectors::cosineSimilarity(dtm[1:1000, , drop = FALSE], 
                                              dtm[1:1000, , drop = FALSE])
dtmsimilarities %>% View

dtm2 <- as.matrix(dtm)

pca <- prcomp(dtm2, scale. = FALSE)
plot(pca)
augment(pca) %>% select(1:6) %>% as_tibble() %>% View

augment(pca) %>%
ggplot(aes(.fittedPC1, .fittedPC2)) + 
geom_point() 

#(for labels) geom_text_repel(aes(label = .rownames))
#saveRDS(pca,"pca_indian_treaties_paragraph_level.rds")
```


##K-Means at the Document Level
 
```{r}

treatycorpus <- list.files("C:/Users/Joshua/Documents/rdata/indian_treaties/treaty-complete",                    pattern = "*.txt",
                   full.names = TRUE)
 
reader <- function(f) {
  require(stringr)
  n <- basename(f) %>% str_replace("\\.txt", "")
  doc <- readr::read_file(f)
  names(doc) <- n
  doc
}

it_files2 <- ifiles(treatycorpus, reader = reader)
it_tokens2 <- itoken(it_files2,
                   tokenizer = tokenizers::tokenize_words)

vocab2 <- create_vocabulary(it_tokens2)

pruned_vocab2 <- prune_vocabulary(vocab2, term_count_min = 10,
term_count_max = 50000)
vectorizer2 <- vocab_vectorizer(pruned_vocab2)

dtm2 <- create_dtm(it_tokens2, vectorizer2)
rownames(dtm2) <- basename(treatycorpus)

parsed_treaties <- readRDS("parsed_treaties.rds")
addyear <- basename(parsed_treaties$file) %>% str_replace("\\.htm", ".txt")


parsed_treaties <- parsed_treaties %>% 
  mutate(document_id = basename(parsed_treaties$file) %>% str_replace("\\.htm", ".txt"))

km <- kmeans(dtm2, centers = 10)

k_clusters <- tibble(document_id = rownames(dtm2),
                     cluster = km$cluster) %>% 
  left_join(parsed_treaties, by = "document_id")

k_clusters %>% arrange(cluster) %>% View

plot(km$cluster)

ggplot(k_clusters, aes(388, 388)) + geom_point()
```


Affinity Propogation Clustering
```{r}

scores_clustering <- similarities

section_names <- lsh_subset(scores_clustering)

lookup <- data_frame(section_names, index = 1:length(section_names))

lookup

scores_clustering <- scores_clustering %>% 
  left_join(lookup, by = c("a" = "section_names")) %>% 
  left_join(lookup, by = c("b" = "section_names")) 

scores_clustering

n <- length(section_names)
m <- sparseMatrix(i = scores_clustering$index.x,
                  j = scores_clustering$index.y,
                  x = scores_clustering$score,
                  dims = c(n, n), symmetric = TRUE)
colnames(m) <- section_names
rownames(m) <- section_names



cluster_cache <- "C:/Users/Joshua/Documents/rdata/indian_treaties/clusters.rds"
if (!file.exists(cluster_cache)) {
  timing <- system.time(
    clu <- apcluster(s = m,
                     maxits = 100e3, convits = 10e3,
                     q = 0,
                     lam = 0.975,
                     seed = 42325, 
                     includeSim = TRUE,
                     )
  )
  saveRDS(clu, cluster_cache)
 } else {
  clu <- readRDS(cluster_cache)
}

clusters <- clu@clusters 
names(clusters) <- names(clu@exemplars)
clusters <- lapply(clusters, names)


exemplars_corpus <- corpus2[names(clusters)]
exemplars_scores <- exemplars_corpus %>% 
  lsh(bands = 40) %>% 
  lsh_candidates() %>% 
  lsh_compare(exemplars_corpus, jaccard_similarity) %>% 
  arrange(desc(score))

#boxplot(exemplars_scores$score)
#hist(exemplars_scores$score)

join_threshold <- 0.15
exemplars_scores <- exemplars_scores %>% 
  filter(score >= 0.19)

#hist(exemplars_scores$score)
```

Creating a Data Frame
```{r}
clusters_df <- clusters %>% 
  seq_along() %>% 
  lapply(function(i) {
    exemplar <- names(clusters)[i]
    doc <- clusters[[i]]
    data_frame(exemplar, doc, cluster_id = i)
  }) %>% 
  bind_rows() %>% 
  group_by(cluster_id) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  arrange(desc(n))

#write_csv(clusters_df, "C:/Users/Joshua/Documents/rdata/indian_treaties/clusters/clusters.csv")
```


```{r}
cluster_df_years <- clusters_df %>%
              mutate(document_id_a = get_treaty(exemplar)) %>%
              mutate(document_id_b = get_treaty(doc)) 
              
cluster_df_years <- left_join(parsed_treaties, cluster_df_years, by = "document_id_a")

cluster_df_years <- subset(cluster_df_years, select = -c(1, 2, 3, 4))

cluster_df_years <- cluster_df_years %>% 
                mutate(exemplar_year = year)


cluster_df_years <- subset(cluster_df_years, select = -c(1, 2, 3, 4))

cluster_df_years <- cluster_df_years %>%
                mutate(document_id_b = document_id_b.y)

cluster_df_years <- subset(cluster_df_years, select = -c(5))

cluster_df_years <- left_join(parsed_treaties, cluster_df_years, by = "document_id_b")

cluster_df_years <- cluster_df_years %>% 
                mutate(doc_year = year)

cluster_df_years <- subset(cluster_df_years, select = -c(1, 2, 3, 4, 5, 6, 7, 8))

cluster_df_years <- na.omit(cluster_df_years)

cluster_df_years <- cluster_df_years %>%
                    mutate(borrow_span = (doc_year - exemplar_year))

#saveRDS(cluster_df_years, "cluster_df_years.rds")
#cluster_df_years <- readRDS("cluster_df_years.rds")

hist(abs(cluster_df_years$borrow_span),
main="Histogram of Paragraph Borrowing Across Time", 
     xlab="Difference in time between exemplar and borrower in years", 
     border="black", 
     col="green",
     xlim=c(0,60),
     ylim= c(0,100),
     las=1,
     #labels =  TRUE,
     breaks= 50)
```

```{r}


plot(h$mids, h$counts, log="y", type='h', lwd=10, lend=2, col= "blue")

```

```{r}
hist(abs(cluster_df_years$borrow_span),
main="Histogram of Paragraph Borrowing Across Time", 
     xlab="Difference in time between exemplar and borrower in years", 
     border="black", 
     col="green",
     xlim=c(0,60),
     ylim= c(0,1200),
     las=1,
     breaks=50)


```

```{r}
#Attempting Histogram with log scale below:

hist(abs(cluster_df_years$borrow_span),
main="Histogram of Paragraph Borrowing Across Time", 
     xlab="Difference in time between exemplar and borrower in years", 
     border="black", 
     col="green",
     xlim=c(0,60),
     ylim= c(0,100),
     las=1,
     #labels =  TRUE,
     breaks= 50)

#NOT YET CHANGED IN CODE ABOVE

cluster_df_years[7] <- lapply(cluster_df_years[7], abs)


qplot(cluster_df_years$borrow_span,
      geom="histogram",
      binwidth = 0.8,  
      main = "Difference in time between exemplar and borrower in years", 
      xlab = "years",  
      fill=I("darkgreen"), 
      col=I("darkgreen"), 
      alpha=I(1),
      xlim=c(0,55))

ggplot(data=cluster_df_years, aes(cluster_df_years$borrow_span)) + 
  geom_histogram(breaks=seq(0, 55, by = 1), 
                 col="black", 
                 fill="darkgreen", 
                 alpha = .9) + 
  labs(title="Difference in Time Between Exemplar and Borrower") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x="Years", y="Count") + 
  xlim(c(0,55)) +
  scale_y_log10(breaks = c(5, 10, 50, 1000)) 

```


```{r}
g <- make_ring(10) %>%
  delete_edges(seq(1, 9, by = 2))
g

plot(g)
g <- make_ring(10) %>%
  delete_edges("8|9")
plot(g)
```


Attempting to use ggraph instead of igraph
```{r}
library(ggraph)


parsed_treaties2 <- readRDS("parsed_treaties.rds")

parsed_treaties2 <- parsed_treaties2 %>%
      mutate(document_id = basename(parsed_treaties2$file) %>% str_replace("\\.htm", ""))

node_df <- subset(parsed_treaties2, select = -c(1, 2, 3, 4))
          
node_df <- node_df[, c(2,1)]

node_df <- node_df %>%
          mutate(treaty_lookup = document_id )

node_df <- node_df %>%
          mutate(decade = year %>% str_extract("\\d{3}"))


node_df$decade[node_df$decade==177] <- "1770s"
node_df$decade[node_df$decade==178] <- "1780s"
node_df$decade[node_df$decade==179] <- "1790s"
node_df$decade[node_df$decade==180] <- "1800s"
node_df$decade[node_df$decade==181] <- "1810s"
node_df$decade[node_df$decade==182] <- "1820s"
node_df$decade[node_df$decade==183] <- "1830s"
node_df$decade[node_df$decade==184] <- "1840s"
node_df$decade[node_df$decade==185] <- "1850s"
node_df$decade[node_df$decade==186] <- "1860s"
node_df$decade[node_df$decade==187] <- "1870s"
node_df$decade[node_df$decade==188] <- "1880s"



G3 <- graph_from_data_frame(d = fd_matches, vertices = node_df, directed = FALSE)



ggraph(G3) +
  geom_edge_link(aes(width = fd_matches$n), alpha = 0.5) +
  scale_edge_width(range = c(0.2, 4)) +
  geom_node_point(aes(color = decade)) 
  
  guide = guide_legend(title = "V"))
 

```

